A weakly structured stem for human origins in Africa

### 2023-02-25 paper.tex
added funding
Shorten section headers

\subsection*{A Late Pleistocene common ancestry for contemporary humans}

@@

\subsection*{Deep but connected population structure within Africa}

@@

\subsection*{Reconciling multiple lines of genetic evidence}

@@

\subsection*{The formation of population structure in Africa}

@@

\subsection*{Contrasting archaic hominin admixture and a weakly structured stem}

@@

We are grateful for the DNA contribution from each participant that enabled
this study; in particular we wish to highlight the generous participation of
the Richtersveld Nama community in South Africa and help from local research
assistants Willem DeKlerk and Hendrik Kaimann. Additional assistance and
community engagement was conducted by Justin Myrick, Chris Gignoux, Caitlen
Uren and Cedric Werely. We thank the African Genome Diversity Project for data
generation, including Tommy Carensten, Deepti Gurdasani, and Manj Sandhu. We
thank Luke Anderson-Trocm\'e and Georgette Femerling for assistance in creating
the map in Figure~\ref{fig:diversity} and Figure \ref{fig:toymodels},
respectively. We thank Nuria Melisa Morales-Garcia for extensive data
visualization discussion and designing Figures \ref{fig:proposed-models} and
\ref{fig:best-fit-models}. This research was supported by an NIH grant
R35GM133531 (to BMH). The content is solely the responsibility of the authors
and does not necessarily represent the official views of the National
Institutes of Health.

>>>>

\subsection*{A Late Pleistocene common ancestry}

@@

\subsection*{A weakly structured stem within Africa}

@@

\subsection*{Reconciling lines of genetic evidence}

@@

\subsection*{Population structure formation in Africa}

@@

\subsection*{Contrasting ancestral structure models}

@@

We are grateful for the DNA contribution from each participant that enabled
this study; in particular we wish to highlight the generous participation of
the Richtersveld Nama community in South Africa and help from local research
assistants Willem DeKlerk and Hendrik Kaimann. Additional assistance and
community engagement was conducted by Justin Myrick, Chris Gignoux, Caitlen
Uren and Cedric Werely. We thank the African Genome Diversity Project for data
generation, including Tommy Carensten, Deepti Gurdasani, and Manj Sandhu. We
thank Luke Anderson-Trocm\'e and Georgette Femerling for assistance in creating
the map in Figure~\ref{fig:diversity} and Figure \ref{fig:toymodels},
respectively. We thank Nuria Melisa Morales-Garcia for extensive data
visualization discussion and designing Figures \ref{fig:proposed-models} and
\ref{fig:best-fit-models}. This research was supported by CIHR project grant 437576,
Natural Sciences and Engineering Research Council of Canada (NSERC) grant RGPIN-2017-04816, 
and the Canada Research Chair program. 
This research was supported by an NIH grant
R35GM133531 (to BMH). The content is solely the responsibility of the authors
and does not necessarily represent the official views of the National
Institutes of Health.
